---
title: "MAX-503 Assignment 2"
output:
  pdf_document: default
  html_notebook: default
---


Save the data set in your working directory
```{r}
setwd("C:/Users/Hema/Desktop/Market Research/Mark Research - Assignment 2/")
getwd()
```

Use read.csv command to read the file and save it in ecomm.df data frame
```{r}
ecomm.df = read.csv("ecommerce-data.csv")
```

Open the data frame and review the column labels
```{r}
ecomm.df
summary(ecomm.df)
```

Use str(ecomm.df) to learn more about the structure of this data set
```{r}
str(ecomm.df)
```

1. How many observations and variables are in the e-commerce data set?
```{r}
dim(ecomm.df)
```
1593 observations & 45 variables

2. Compute a frequency table for the country of origin for site visits. After the United States, which country had the most visitors?
```{r}
table(ecomm.df$country)
```
Canada had the second most visitors with 62 visitors.

3. Compute a two-way frequency table for the intent to purchase (intentWasPlanningToBuy) broken out by user profile.
```{r}
table(ecomm.df$intentWasPlanningToBuy,ecomm.df$profile)
```

4. What are the proportions of parents who intended to purchase? The proportions of teachers who did?
```{r}
# step 1.get the rows of people who intend to purchase and profile
intent_table <- table(ecomm.df$intentWasPlanningToBuy, ecomm.df$profile)
```
```{r}
#step 2.what is the proportion of parents   
#(totals of parents who intend to purchase / totals of people who intend to purchase)
sum(intent_table[3:4,5])/sum(intent_table[3:4,])   #->proportion of parents
```
59.73% of users who intend to purchase are parents.

```{r}
#step 3.what is the proportion of teachers
#(totals of teachers who intend to purchase / totals of people who intend to purchase)
sum(intent_table[3:4,8])/sum(intent_table[3:4,])   #->proportion of teachers
```
10.84% of users who intend to purchase are teachers.

5. Among US states (recorded in the variable region), which state had the most visitors and how many?
```{r}
US_States_Data <-ecomm.df[which(ecomm.df$country=='United States'),]
table(US_States_Data$region)
```
Texas had the most visitors with 94 visitors.

6. Solve the previous problem for the state with the most visitors, using the which.max() function (or repeat the same answer, if you already used it).
```{r}
which.max(table(US_States_Data$region))
```

7. Draw a histogram for the number of visits to the site (behavNumVisits). Adjust it for more detail in the lower values. Color the bars and add a density line.
```{r}
hist(ecomm.df$behavNumVisits,main="Number of Visits to Site",
     xlab="Number of Visits",ylab="Frequency",breaks = 30, col = "lightblue",freq = FALSE)
lines(density(ecomm.df$behavNumVisits, bw=10),type="l",lwd=10, col = "tomato3")
```

8. Draw a horizontal boxplot for the number of site visits.
```{r}
boxplot(ecomm.df$behavNumVisits, xlab="Number of Visits", yaxt="n",
        main="Number of Site Visits", horizontal=TRUE)
```

9. Draw a boxplot for site visits broken out with a unique row for each profile type.
(Note: if the chart margins make it unreadable, try the following command before plotting: par(mar=c(3, 12, 2, 2)).
After plotting, you can use the command par(mar=c(5, 4, 4, 2)+ 0.1) to reset the chart margins.)
```{r}
par(mar=c(5, 13, 2, 2))
boxplot(ecomm.df$behavNumVisits~ecomm.df$profile,main="Number of Site Visits", horizontal = TRUE,
        xlab = "Number of Visits", ylab="Profile", las=1)
```
